\section{Design Revisions}
\label{sec:missingmember}

%This section discusses various revisions and modifications which could be made to the design to improve performance.

%\subsection{Missing Member}
%\label{sec:missingmember}

A critical oversight made during initial design and construction of the truss significantly reduced performance.
An important member (member \emph{M1} in figure \ref{fig:diagram}) was neglected.
%
When evaluating truss designs to resist vertical deflection and maximize efficiency, cantilever end conditions were assumed. 
As such, the displacement at joint \emph{J1} (figure \ref{fig:diagram}) was assumed to be negligible.
By failing to include member \emph{M1}, there was no structure able to sufficiently resist deflection of joint \emph{J1}, invalidating many assumptions and the results related to overall deflection.

A finite element analysis may be used to estimate the performance gained by adding the additional member. 
Using \emph{SolidWokrs} as the simulator, two tests were performed, one with the additional member and one without.
The SolidWorks FEM predicted a deflection of 3.95 mm for the design without member \emph{M1}; comparable to the deflection observed during testing of 3.1 mm. 
By adding member \emph{M1}, the predicted deflection decreased to 1.66 mm; more than doubling the efficiency of the structure.
Given this result, adding the member is likely the single most important action which could be taken to improve the overall efficiency performance of the structure.

%Terrible, need to reword

\section{Conclusion}

%This conclusion is pretty bad:

Using analytical and finite element analysis, two separate truss structures were designed  for the vertical and horizontal planes, each having slightly different requirements and constraints.
Each was found to be optimal (at least within the context of designs considered) for resisting bending in the plane of interest. 
A final truss structure was designed, analyzed and constructed which incorporated both truss components. %Yuck
Based on mechanical testing, finite element models were found to predict vertical deflection reasonably well but performed less well when predicting horizontal deflection.
%More?

%Include:
%	- ?
%	- Analysis not terribly accurate
%	- Could be improved by adding member
%	- Likely the optimal design (?)